---
title: "Practical Machine Learning"
author: "Ietje Penninga"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

For Machine Learning class a dataset was obtained by:  `http://groupware.les.inf.puc-rio.br/har#ixzz3gbvAGgXX`. 

Their article on machine learning is available: 

Velloso, E.; Bulling, A.; Gellersen, H.; Ugulino, W.; Fuks, H. Qualitative Activity Recognition of Weight Lifting Exercises. Proceedings of 4th International Conference in Cooperation with SIGCHI (Augmented Human '13) . Stuttgart, Germany: ACM SIGCHI, 2013.

The data contains a set of measurements on 6 atlethes that perform a series of weight lifting exercises. The way they perform the exercise is classified by an expert as A (= correct) , or as B:E (=various errors). Task is to determine based on the variables measured how the exercise is executed: A,B,C,D or E. 

The training set consists of a number of measurements and a classification. 
Upon first analysis of the data it appears that the first 6 columns contain information about the atlethe and time and date of the measeurement. Of the other variables, there are some variables that generate a NA measurement in about 90% of the cases. These variables were therefore considered unsuitable to build the model on, and were not used in subsequent modelling. 

After this reduction of variables an analysis was performed on the variability of the variables. 
 The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
